\section{Our model and approach}
\label{sec:approach}
We now develop our model and use it to specify our problem more
precisely. We then present our algorithm to address our ailment
prediction problem.
\subsection{\tmatam: Modeling Health Topics over Time}
\label{subsec:model}
We propose \tmatam that builds on top of \atam and \tmlda.
We first convert inferences of \atam over a single document to associate with a given set of documents $D_g^t$, an ailment
distribution, $\Theta_g^t$. We then go on to find \seasons. We model ailment transitions within each \season and when \change is 
encountered we update these transitions.  This is a fresh departure
from existing solutions that operate in a \season-agnostic fashion\cite{DBLP:conf/kdd/WangAB12}.
\tmatam, at its heart, solves the following equation.
\begin{equation}
A_g^{t}\approx A_g^{t-1}.M
\end{equation}
where
\begin{equation}
A_g^{t-1}=\begin{pmatrix}\Theta_g^1\\\vdots\\\Theta_g^t\end{pmatrix},\,A_g^t=\begin{pmatrix}\Theta_g^2\\\vdots\\\Theta_g^{t+1}\end{pmatrix}%d_g^{t-1}=\begin{pmatrix}P_1\\\vdots\\P_t\end{pmatrix},\,d_g^t=\begin{pmatrix}P_2\\\vdots\\P_{t+1}\end{pmatrix}
\end{equation}
$M$ is an unknown transition matrix which has to be learned.
To obtain the transition matrix $M$, we solve the following least squares problem.
\[
\min_M\|A_g^t- A_g^{t-1}.M\|_F
\]
\subsection{Ailment prediction problem}
\label{subsec:problem}
We are now ready to visit our problem: Given a set of
documents $D_g^{t_{i-1}}$ formed by tweets originating from a region
$g \in G$ during time period $t_{i-1}$, predict $\Theta_g^{t_i}$, the
ailment distribution of documents in $D_g^{t_i}$, corresponding to
posts from $g$ in period $t_i$ from $\Theta_g^{t_{i-1}}$, the ailment
distribution of document $D_g^{t_{i-1}}$ corresponding to posts from
$g$ during period $t_{i-1}$.
\subsection{Algorithm}
\label{subsec:tmalg}
Algorithm~\ref{alg:tmatam} contains the steps of our solution. It has 
two main parts:  \change \emph{\texttt{detection}} and \emph{\texttt{ ailment prediction}}. 
We first describe how \changes are detected then we show how ailment topics being discussed in twitter 
are predicted over time.
\paragraph{Change Point Detection}
We use $\mf Z$ to refer to the set of all health-related and non-health 
related topics. For each region $g \in \mf G$ (Line~\ref{alg:line:start}) 
we first run \atam over the full time period $D_g$ (Line~\ref{alg:line:atam}).
Next for each period $t\in \mf T$ (Line~\ref{alg:line:tstart}), 
we use the output of \atam over $D_g$ to generate 
topic distribution $\Theta_g^t$ (Lines~\ref{alg:line:createThetaStart}--
\ref{alg:line:createThetaEnd}).
Next we examine the  \emph{Bhattacharya Distance} between consecutive distributions
$\Theta_g^{t-1}$ and $\Theta_g^t$ of the region $g$ 
to identify the most significant change point, $t_c$ (Line~\ref{alg:line:ThetaDiff}).
The time period $t_c$ is termed as the \change for
region $g$. The time periods preceding and succeding \change are termed as \seasons.
\paragraph{Intra Homogenous Time Period Ailment Prediction}
We outline in lines~\ref{alg:line:predStart}--\ref{alg:line:predEnd} 
of Algorithm~\ref{alg:tmatam} the steps undertaken. 
\begin{algorithm}[t]
\caption{TM-ATAM: \change Detection and Training Ailment Distribution Predictor}
\label{alg:tmatam}
\begin{algorithmic}[1]
 \ForAll {$g \in G$}\label{alg:line:start}
 \State Run ATAM on $D_g$\label{alg:line:atam}
 \ForAll  {$t \in \mf T$}:\label{alg:line:tstart}
 \ForAll {$z \in \mf Z$}:\label{alg:line:createThetaStart}
 \State $\Theta_g^t[z] \leftarrow 0$
 \EndFor
 \ForAll {$d \in D_g^t$}:
 \ForAll {$w \in d$}:
 \State $z \gets topic(w)$
 \State $\Theta_g^t[z] \gets \Theta_g^t[z] + \frac{1}{|d|\times |D_g^t|}$
 \EndFor
 \EndFor\label{alg:line:createThetaEnd}
 \EndFor
 \State $\displaystyle t_{c} = \argmax_t{\ m(\Theta_g^{t-1},\ \Theta_g^{t})}$\label{alg:line:ThetaDiff}
 \State $pre = [t_1\ ,\ t_{c-1}]$\label{alg:line:buildSeasonPre} 
 \State $post = [t_{c}\ , \ t_{|\mf T|}]$\label{alg:line:buildSeasonPost} 
 \ForAll {$s \in \{pre,\ post\}$}:\label{alg:line:predStart}
 \State $A_g^t\approx A_g^{t-1}.M$
 \State $M =(A_g^{t-1\intercal}A_g^{t-1})^{-1}A_g^{t-1\intercal}A_g^t$
 %\State $M = A_g^{t-1}\textsuperscript{\textdagger}A_g^t=(A_g^{t-1\intercal}A_g^{t-1})^{-1}A_g^{t-1\intercal}A_g^t$
 \EndFor\label{alg:line:predEnd}
\EndFor\label{alg:line:end}
\end{algorithmic}
\end{algorithm}
